\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\large
In recent years, the Vietnamese Ministry of Education — like many institutions worldwide — has placed greater emphasis on strengthening accreditation processes in higher education, recognizing their critical role in ensuring and maintaining educational quality standards. However, preparing accreditation reports remains largely manual, time‑consuming, and often inconsistent across departments and institutions. To address these challenges, this thesis proposes an AI‑Based System for Accreditation Report Quality Enhancement designed to automatically analyze report documents, suggest standardized structures, and provide dynamic evaluation forms to assist secretaries and inspectors.

Currently, report preparation typically relies on editing Microsoft Word documents and managing supporting evidence and related materials in tools such as Google Drive, which lack specialized features for accreditation workflows. This often leads to fragmented formatting, repetitive edits, and limited collaboration. To overcome these issues, the proposed system can parse DOCX files, detect missing sections, and generate recommendations aligned with accreditation guidelines.

The system is built with a modern, practical technology stack — including Vite.js for a responsive front‑end, Node.js for back‑end APIs, MongoDB for structured data storage, and Supabase for secure document management. By applying natural language processing techniques, it can identify structural gaps and suggest standardized headings and templates.

Overall, this project demonstrates how AI and modern web technologies can make accreditation reporting more efficient, reliable, and consistent, paving the way for future enhancements and deeper integration.

